HPC--101\\Onboarding

### 2020-10-15 hpc_101/sections/01_intro.tex
Changed mentioned of UH-HPC to Mana Changed SLURM to Slurm as it is no longer an acronym.

\section[University of Hawai'i High Performance Compute Cluster]{University of Hawai'i High Performance Compute Cluster}
\begin{frame}
    \frametitle{University of {\hawaii} High Performance Compute Cluster}
    \begin{itemize}
    \item The University~of~{\hawaii} High Performance Compute Cluster~({\uhhpc}) is \textbf{free} to use for all active faculty, staff, and students affiliated with the University of {\hawaii}
    \item Community acquired nodes are equally accessible to all users
    \item Nodes purchased through the {\textbf{condo program}} are shared with the community, but priority is given to the node owner and their agents
		\item Nodes may be {\textbf{leased}} from the community pool
		\item Additional permanent storage can be leased by faculty \& staff
    \end{itemize}
		\begin{block}{UH-HPC Resource Summary}
  \begin{table}
    \centering
    \resizebox{\textwidth}{!}{%
      \begin{tabular}{l||l||l||l||l||l||l||l}
      %  \multicolumn{8}{c}{ {\large {\textbf{UH-HPC Resource Summary} } } } \\ 
			\toprule

@@

\subsection{Condo Program \& Leasing}
\begin{frame}
  \frametitle{What is the Condo Program \& leasing?}
	\begin{block}{Condo Program}\scriptsize
		\begin{itemize}
		\item The condo program allows faculty \& staff to purchase nodes and have them integrated with the UH-HPC
		\item Condo nodes can take advantage of networking and storage infrastructure that one may not typically have access to
		\item Condo nodes are managed and maintained by ITS staff
		\item No maintenance fee will be assessed until the node is off warranty (typically five years)
		\end{itemize}
	\end{block}
	\begin{block}{Leasing}\scriptsize
		\begin{itemize}
		\item Nodes leased from the community can have a contract period from one month, up to one year
		\item Node lessees are provided priority access to their leased hardware
		\item Leases are not considered an equipment purchase
		\end{itemize}
	\end{block}
\end{frame}

\subsection{Storage}
\begin{frame}
  \frametitle{Storage}
  The UH-HPC has two classes and three types of storage that users can potentially access.\\Each type of storage has their own attributes and restrictions
	\begin{columns}
		\begin{column}{0.46\textwidth}
		\begin{block}{Free Storage}
			\begin{enumerate}
			\item Permanent Storage
				\begin{itemize}
				\item Home Storage
				\item Group/Lab Storage
				\end{itemize}
			\item Scratch Storage
				\begin{itemize}
%				\item {\lustre}(TBD)
				\item Network File System (NFS)
				\end{itemize}
		\end{enumerate}
		\end{block}
		\end{column}
		\begin{column}{0.46\textwidth}
		\begin{block}{For Fee Storage}
			\begin{enumerate}
				\item Long Term Storage (LTS)
		\end{enumerate}
		\end{block}
		\end{column}
	\end{columns}      
\end{frame}

\begin{frame}
  \frametitle{Permanent Storage}
  \begin{enumerate}
  \item Home Storage
    \begin{itemize}
    \item {\textbf{Purpose}}: Personal storage for applications and active data that needs to persist on the UH-HPC
    \end{itemize}
  \item Group/Lab Storage
    \begin{itemize}
    \item {\textbf{Purpose}}: Group/Lab storage allows users to share data \& applications with a need for persistence on the UH-HPC
    \end{itemize}
  \end{enumerate}
~\\
  Permanent storage options on the UH-HPC have the following attributes:
  \begin{itemize}
  \item 50 GB default quota with a max quota of 300 GB
  \item Quota increases are re-evaluated annually
  \item Available on all nodes
  \item Freely available to users
  \end{itemize}

@@

\begin{frame}
  \frametitle{Scratch Storage}
  \begin{enumerate}
%    \item {\lustre (TBD)}
%      \begin{itemize}
%      \item High performance parallel file system 
%      \item 50 TB quota
%      \end{itemize}
    \item NFS
      \begin{itemize}
%      \item Not a parallel file system
      \item 5 TB quota
      \end{itemize}
  \end{enumerate}
~\\
  Scratch file systems on the UH-HPC have the following attributes:
  \begin{itemize}
  \item \textbf{Purge policy} -- 10 days based on file modify time
  \item Available on all nodes
  \item Freely available to users
  \end{itemize}

>>>>

\section[University of Hawai'i High Performance Compute Cluster]{University of Hawai'i High Performance Compute Cluster}
\begin{frame}
    \frametitle{University of {\hawaii} High Performance Compute Cluster}
    \begin{itemize}
    \item The University~of~{\hawaii} High Performance Compute Cluster - \textbf{\mana} (formerly~known~as~the~{\uhhpc}) is \textbf{free} to use for all active faculty, staff, and students affiliated with the University of {\hawaii}
    \item Community acquired nodes are equally accessible to all users
    \item Nodes purchased through the {\textbf{condo program}} are shared with the community, but priority is given to the node owner and their agents
		\item Nodes may be {\textbf{leased}} from the community pool
		\item Additional permanent storage can be leased by faculty \& staff
    \end{itemize}
		\begin{block}{Mana Resource Summary}
  \begin{table}
    \centering
    \resizebox{\textwidth}{!}{%
      \begin{tabular}{l||l||l||l||l||l||l||l}
      %  \multicolumn{8}{c}{ {\large {\textbf{UH-HPC Resource Summary} } } } \\ 
			\toprule

@@

\subsection{Condo Program \& Leasing}
\begin{frame}
  \frametitle{What is the Condo Program \& leasing?}
	\begin{block}{Condo Program}\scriptsize
		\begin{itemize}
		\item The condo program allows faculty \& staff to purchase nodes and have them integrated with {\mana}
		\item Condo nodes can take advantage of networking and storage infrastructure that one may not typically have access to
		\item Condo nodes are managed and maintained by ITS staff
		\item No maintenance fee will be assessed until the node is off warranty (typically five years)
		\end{itemize}
	\end{block}
	\begin{block}{Leasing}\scriptsize
		\begin{itemize}
		\item Nodes leased from the community can have a contract period from one month, up to one year
		\item Node lessees are provided priority access to their leased hardware
		\item Leases are not considered an equipment purchase
		\end{itemize}
	\end{block}
\end{frame}

\subsection{Storage}
\begin{frame}
  \frametitle{Storage}
  {\mana} has two classes and three types of storage that users can potentially access.\\Each type of storage has their own attributes and restrictions
	\begin{columns}
		\begin{column}{0.46\textwidth}
		\begin{block}{Free Storage}
			\begin{enumerate}
			\item Permanent Storage
				\begin{itemize}
				\item Home Storage
				\item Group/Lab Storage
				\end{itemize}
			\item Scratch Storage
				\begin{itemize}
%				\item {\lustre}(TBD)
				\item Network File System (NFS)
				\end{itemize}
		\end{enumerate}
		\end{block}
		\end{column}
		\begin{column}{0.46\textwidth}
		\begin{block}{For Fee Storage}
			\begin{enumerate}
				\item Long Term Storage (LTS)
		\end{enumerate}
		\end{block}
		\end{column}
	\end{columns}      
\end{frame}

\begin{frame}
  \frametitle{Permanent Storage}
  \begin{enumerate}
  \item Home Storage
    \begin{itemize}
    \item {\textbf{Purpose}}: Personal storage for applications and active data that needs to persist on {\mana}
    \end{itemize}
  \item Group/Lab Storage
    \begin{itemize}
    \item {\textbf{Purpose}}: Group/Lab storage allows users to share data \& applications with a need for persistence on {\mana}
    \end{itemize}
  \end{enumerate}
~\\
  Permanent storage options on {\mana} have the following attributes:
  \begin{itemize}
  \item 50 GB default quota with a max quota of 300 GB
  \item Quota increases are re-evaluated annually
  \item Available on all nodes
  \item Freely available to users
  \end{itemize}

@@

\begin{frame}
  \frametitle{Scratch Storage}
  \begin{enumerate}
%    \item {\lustre (TBD)}
%      \begin{itemize}
%      \item High performance parallel file system 
%      \item 50 TB quota
%      \end{itemize}
    \item NFS
      \begin{itemize}
%      \item Not a parallel file system
      \item 5 TB quota
      \end{itemize}
  \end{enumerate}
~\\
  Scratch file systems on {\mana} have the following attributes:
  \begin{itemize}
  \item \textbf{Purge policy} -- 10 days based on file modify time
  \item Available on all nodes
  \item Freely available to users
  \end{itemize}

### 2020-10-15 hpc_101/sections/03_policies.tex
Changed mentioned of UH-HPC to Mana Changed SLURM to Slurm as it is no longer an acronym.

\section[UH-HPC Usage Policies]{UH-HPC Usage Policies}

\subsection{Login nodes \& DTN nodes}
\begin{frame}
\frametitle{Login nodes \& DTN nodes}
\begin{block}{}
The following actions are acceptable on the shared systems in the UH-HPC:
\begin{enumerate}
\item File/Directory management [ Login \& DTN nodes ]
\item Text editing with a text editor: vi/vim, emacs, nano [ Login \& DTN nodes ]
\item Transferring files to and from the cluster (scp, rsync, SFTP, globus, aspera, lftp, etc.) [ Login \& DTN nodes ]
\item Shall be used to submit batch and interactive jobs [Login nodes]
\item SSH shell access [ Login \& DTN nodes ]
\end{enumerate}
\end{block}

@@

\subsection{User Account Life Cycle}
\begin{frame}
\frametitle{User Account Life Cycle}
\begin{enumerate}
\item Accounts that are idle for 120 days will be locked
\item Accounts that have been locked can be unlocked upon request with no further action then emailing us a request to unlock their account
\item Accounts that are idle for a total of 180 days will be purged from the cluster
\item Users that have been purged may request a reactivation of their account, but may be required to take a quiz to confirm retention of how to use the UH-HPC
\item Users that will be leaving UH or are no longer active at UH, will need to have an active UH faculty/staff member in good standing, request a UH-HPC account extension.
\end{enumerate}
\end{frame}

\begin{frame}
\frametitle{Where to find all UH-HPC specific policies}
\begin{enumerate}
%\item \href{http://www.hawaii.edu/infotech/policies/itpolicy.html\#appendixa}{Chapter 708, Hawaii Revised Statutes}
%\item \href{http://www.hawaii.edu/infotech/policies/itpolicy.html}{University of Hawaii Executive Policy E2.210}
\item \href{http://go.hawaii.edu/GSY}{Common systems \& Storage}
\item \href{http://go.hawaii.edu/0SG}{User Account life cycle}
\item \href{http://go.hawaii.edu/WSG}{Security}
\item \href{http://go.hawaii.edu/YKG}{For lease storage}
\item \href{http://go.hawaii.edu/GK0}{Condo Program \& Off Warranty condo nodes}
%% \item \href{https://docs.google.com/document/d/1mGcCAsmzGT_hWXLcUNfT2LUwiggCnhqrln32k0IGZZI/}{Special allocations}
\end{enumerate}
\end{frame}
%
%\begin{frame}
%\frametitle{Login Node Usage Policy}\footnotesize
%The login nodes are a shared resource and are the only access to the cluster for hundreds of user and are meant to provide the following functionality for all users: 
%\begin{itemize}
%\item Providing ssh shell access 
%\item Facilitate the transfer files to and from the cluster:\\Globus, sftp, scp, rsync
%\item Launching and monitoring SLURM jobs (batch and interactive)
%\item Modifying text files with a text editor: vi/vim, emacs, nano
%\end{itemize}
%\bigskip
%\begin{itemize}
%\item[--] If we identify or are notified that a user is running computation on the login nodes, the application will be killed
%\item[--] If we determine that a user repeatedly violates the login node policy, even after being warned, the repeat offender can have their cluster account disabled
%\end{itemize}
%\btVFill
%\begin{center}
%\footnotesize \textbf{\emph{Login node usage policy is subject to change~\\Users will be notified via email prior to changes taking effect}}
%\end{center}
%\end{frame}
%
%
%\subsection{Lustre Filesystem Purge Policies}
%\begin{frame}
%\frametitle{{\lustre} Filesystem Purge Policies}
%Due to users not having any quotas on the {\lustre} filesystem, we need some policy in place which removes older files from the system.  To accomplish this, we have implemented a purge policy.
%
%\begin{itemize}
%\item What in \ctilde/lus/ is subject to the purge policy?
   %\begin{itemize}
   %\item \textbf{Answer:} Everything but directories.
   %\end{itemize}
%\item When will my files be purged?
  %\begin{itemize}  
    %\item \textbf{Answer:} Files greater than or equal to 1 Megabyte in size or are empty (0 bytes) that are 35 days old
    %\item \textbf{Answer:} Files between 1 byte and 1 Megabyte in size that are 120 days old
  %\end{itemize}
%\item What is the age based on?
   %\begin{itemize}
   %\item \textbf{Answer:} Age of file is based on creation time
   %\end{itemize}
   %
%%\item How frequently are files for purged?
%%   \begin{itemize}
%%   \item \textbf{Answer:} Taking into account the fill rate of the {\lustre} filesystem, a purge is performend as usage approaches 80\%.
%%   \end{itemize}
%\end{itemize}
%\btVFill
%\begin{center}
%\footnotesize \textbf{\emph{Purge policy is subject to change~\\Users will be notified via email prior to changes taking effect}}
%\end{center}
%\end{frame}
%
%
%
%\begin{frame}
  %\frametitle{How to check file age for purge}
  %A tool is available on the cluster called age\_check.  This tool will list all files that are older than the defined date you set.
%\begin{semiverbatim}\tiny \texttt
  %$[$root@login-0001 \ctilde$]$\$ age\_check -h
  %
  %Usage:
  %age\_check [-s] [-z] [-d] [-f] [-a <age cutoff>] [-p <path]
%
%
  %Options:
%
  %-s -- Sort output
  %
  %-d -- display creation date per file
  %
  %-z -- display size in bytes per file
  %
  %-f -- Do not exclude files between 1 byte and 1 MB
  %
  %-a age -- Lists files that were created at least age days ago (default is 20 days)
  %
  %-p path -- Directory to check in (default is /lus/scratch/root)
%
  %
  %Example:
  %age\_check -a 30  
%
%\end{semiverbatim}
%
%\end{frame}

>>>>

\section[Mana Usage Policies]{Mana Usage Policies}

\subsection{Login nodes \& DTN nodes}
\begin{frame}
\frametitle{Login nodes \& DTN nodes}
\begin{block}{}
The following actions are acceptable on the shared systems in {\mana}:
\begin{enumerate}
\item File/Directory management [ Login \& DTN nodes ]
\item Text editing with a text editor: vi/vim, emacs, nano [ Login \& DTN nodes ]
\item Transferring files to and from the cluster (scp, rsync, SFTP, globus, aspera, lftp, etc.) [ Login \& DTN nodes ]
\item Shall be used to submit batch and interactive jobs [Login nodes]
\item SSH shell access [ Login \& DTN nodes ]
\end{enumerate}
\end{block}

@@

\subsection{User Account Life Cycle}
\begin{frame}
\frametitle{User Account Life Cycle}
\begin{enumerate}
\item Accounts that are idle for 120 days will be locked
\item Accounts that have been locked can be unlocked upon request with no further action then emailing us a request to unlock their account
\item Accounts that are idle for a total of 180 days will be purged from the cluster
\item Users that have been purged may request a reactivation of their account, but may be required to take a quiz to confirm retention of how to use {\mana}
\item Users that will be leaving UH or are no longer active at UH, will need to have an active UH faculty/staff member in good standing, request a {\mana} account extension.
\end{enumerate}
\end{frame}

\begin{frame}
\frametitle{Where to find all Mana specific policies}
\begin{enumerate}
%\item \href{http://www.hawaii.edu/infotech/policies/itpolicy.html\#appendixa}{Chapter 708, Hawaii Revised Statutes}
%\item \href{http://www.hawaii.edu/infotech/policies/itpolicy.html}{University of Hawaii Executive Policy E2.210}
\item \href{http://go.hawaii.edu/GSY}{Common systems \& Storage}
\item \href{http://go.hawaii.edu/0SG}{User Account life cycle}
\item \href{http://go.hawaii.edu/WSG}{Security}
\item \href{http://go.hawaii.edu/YKG}{For lease storage}
\item \href{http://go.hawaii.edu/GK0}{Condo Program \& Off Warranty condo nodes}
%% \item \href{https://docs.google.com/document/d/1mGcCAsmzGT_hWXLcUNfT2LUwiggCnhqrln32k0IGZZI/}{Special allocations}
\end{enumerate}
\end{frame}
%
%\begin{frame}
%\frametitle{Login Node Usage Policy}\footnotesize
%The login nodes are a shared resource and are the only access to the cluster for hundreds of user and are meant to provide the following functionality for all users: 
%\begin{itemize}
%\item Providing ssh shell access 
%\item Facilitate the transfer files to and from the cluster:\\Globus, sftp, scp, rsync
%\item Launching and monitoring SLURM jobs (batch and interactive)
%\item Modifying text files with a text editor: vi/vim, emacs, nano
%\end{itemize}
%\bigskip
%\begin{itemize}
%\item[--] If we identify or are notified that a user is running computation on the login nodes, the application will be killed
%\item[--] If we determine that a user repeatedly violates the login node policy, even after being warned, the repeat offender can have their cluster account disabled
%\end{itemize}
%\btVFill
%\begin{center}
%\footnotesize \textbf{\emph{Login node usage policy is subject to change~\\Users will be notified via email prior to changes taking effect}}
%\end{center}
%\end{frame}
%
%
%\subsection{Lustre Filesystem Purge Policies}
%\begin{frame}
%\frametitle{{\lustre} Filesystem Purge Policies}
%Due to users not having any quotas on the {\lustre} filesystem, we need some policy in place which removes older files from the system.  To accomplish this, we have implemented a purge policy.
%
%\begin{itemize}
%\item What in \ctilde/lus/ is subject to the purge policy?
   %\begin{itemize}
   %\item \textbf{Answer:} Everything but directories.
   %\end{itemize}
%\item When will my files be purged?
  %\begin{itemize}  
    %\item \textbf{Answer:} Files greater than or equal to 1 Megabyte in size or are empty (0 bytes) that are 35 days old
    %\item \textbf{Answer:} Files between 1 byte and 1 Megabyte in size that are 120 days old
  %\end{itemize}
%\item What is the age based on?
   %\begin{itemize}
   %\item \textbf{Answer:} Age of file is based on creation time
   %\end{itemize}
   %
%%\item How frequently are files for purged?
%%   \begin{itemize}
%%   \item \textbf{Answer:} Taking into account the fill rate of the {\lustre} filesystem, a purge is performend as usage approaches 80\%.
%%   \end{itemize}
%\end{itemize}
%\btVFill
%\begin{center}
%\footnotesize \textbf{\emph{Purge policy is subject to change~\\Users will be notified via email prior to changes taking effect}}
%\end{center}
%\end{frame}
%
%
%
%\begin{frame}
  %\frametitle{How to check file age for purge}
  %A tool is available on the cluster called age\_check.  This tool will list all files that are older than the defined date you set.
%\begin{semiverbatim}\tiny \texttt
  %$[$root@login-0001 \ctilde$]$\$ age\_check -h
  %
  %Usage:
  %age\_check [-s] [-z] [-d] [-f] [-a <age cutoff>] [-p <path]
%
%
  %Options:
%
  %-s -- Sort output
  %
  %-d -- display creation date per file
  %
  %-z -- display size in bytes per file
  %
  %-f -- Do not exclude files between 1 byte and 1 MB
  %
  %-a age -- Lists files that were created at least age days ago (default is 20 days)
  %
  %-p path -- Directory to check in (default is /lus/scratch/root)
%
  %
  %Example:
  %age\_check -a 30  
%
%\end{semiverbatim}
%
%\end{frame}
